---
title: "Demo-data workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo-data workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This article shows the full CCE workflow on bundled synthetic data:

1. create normalized source tables
2. build an analysis-ready cohort
3. estimate a VS-mode comparison
4. run SOC-only projection scenarios
5. export results for reporting

## Generate the example data

```{r}
library(cce)

demo <- cce_demo_data(n = 240, seed = 42)
names(demo)
```

The demo generator returns the four normalized tables plus a ready-made
analysis dataset.

```{r}
str(demo$analysis_data)
```

## Round-trip the analysis specification

```{r}
spec_path <- tempfile(fileext = ".yml")
write_cce_spec(demo$spec, spec_path)
roundtrip_spec <- read_cce_spec(spec_path)
roundtrip_spec$covariates
```

## Rebuild the analysis dataset from normalized tables

```{r}
analysis <- build_analysis_dataset(
  patient_baseline = demo$patient_baseline,
  treatment_episodes = demo$treatment_episodes,
  outcomes = demo$outcomes,
  biomarkers = demo$biomarkers,
  spec = roundtrip_spec
)

head(analysis)
```

## VS-mode estimation

```{r}
vs_fit <- fit_cce_vs(
  data = analysis,
  arm = "arm",
  time = "time",
  event = "event",
  covariates = c("age", "sex", "stage_or_risk", "ps"),
  subgroup = "subgroup",
  tau = 365,
  landmark_times = c(180, 365),
  bootstrap = 20,
  seed = 100
)

summary(vs_fit)
```

```{r, fig.width = 7, fig.height = 4}
plot(vs_fit, method = "gformula", subgroup = "All")
```

The tidy effects table is designed to feed downstream reports or dashboards.

```{r}
head(as_effects_df(vs_fit))
```

Diagnostics are returned in a machine-readable table.

```{r}
head(as_diagnostics_df(vs_fit))
```

## SOC-only projection

```{r}
soc_fit <- project_soc_only(
  data = analysis,
  arm = "arm",
  soc_level = "SOC",
  time = "time",
  event = "event",
  subgroup = "subgroup",
  tau = 365,
  hr_scenarios = c(0.65, 0.80, 1.00),
  target_delta_rmst = 30,
  prior_mean_log_hr = log(0.8),
  prior_sd_log_hr = 0.25,
  bootstrap = 20,
  seed = 200
)

summary(soc_fit)
```

```{r, fig.width = 7, fig.height = 4}
plot(soc_fit, subgroup = "All")
```

```{r}
head(as_effects_df(soc_fit))
```

## Export files

```{r}
out_dir <- tempfile(pattern = "cce-demo-")
write_cce_results(vs_fit, out_dir)
list.files(out_dir)
```

The written directory contains:

- `results.json`
- `curves.csv`
- `effects.csv`
- `diagnostics.csv`

## Notes

The bundled demo is useful for package validation and documentation. For public
patient-level data, see the companion article on `survival::veteran`.
