---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
if (requireNamespace("pkgload", quietly = TRUE)) {
  if (file.exists("DESCRIPTION")) {
    pkgload::load_all(".", export_all = FALSE, helpers = FALSE, attach_testthat = FALSE)
  } else if (file.exists("../DESCRIPTION")) {
    pkgload::load_all("..", export_all = FALSE, helpers = FALSE, attach_testthat = FALSE)
  } else {
    library(cce)
  }
} else {
  library(cce)
}
```

## Overview

`cce` has two main workflows:

- `fit_cce_vs()` for A versus SOC comparisons
- `project_soc_only()` for assumption-based SOC-only projections

Both workflows are built around the same output contract:

- survival curves
- effect tables
- diagnostics tables
- `results.json` metadata for audit and reporting

## Generate demo data

```{r}
demo <- cce_demo_data(n = 220, seed = 42)
names(demo)
```

The demo helper returns normalized source tables and a ready-made analysis
dataset.

```{r}
head(demo$analysis_data)
```

## Define and round-trip the analysis contract

```{r}
spec_path <- tempfile(fileext = ".yml")
write_cce_spec(demo$spec, spec_path)
spec <- read_cce_spec(spec_path)
spec$covariates
```

## Validate and assemble the analysis dataset

```{r}
validate_cce_tables(
  patient_baseline = demo$patient_baseline,
  treatment_episodes = demo$treatment_episodes,
  outcomes = demo$outcomes,
  biomarkers = demo$biomarkers,
  spec = spec
)
```

```{r}
analysis <- build_analysis_dataset(
  patient_baseline = demo$patient_baseline,
  treatment_episodes = demo$treatment_episodes,
  outcomes = demo$outcomes,
  biomarkers = demo$biomarkers,
  spec = spec
)
```

```{r}
profile_cce_dataset(
  data = analysis,
  arm = "arm",
  time = "time",
  event = "event",
  subgroup = "subgroup"
)
```

## Fit a VS comparison

```{r}
vs_fit <- fit_cce_vs(
  data = analysis,
  arm = "arm",
  time = "time",
  event = "event",
  covariates = c("age", "sex", "stage_or_risk", "ps"),
  subgroup = "subgroup",
  tau = 365,
  landmark_times = c(180, 365),
  bootstrap = 10,
  seed = 100
)

summary(vs_fit)
```

```{r}
head(as_effects_df(vs_fit))
```

The VS output includes results from:

- `gformula`
- `iptw_km`
- `iptw_cox`

```{r}
head(as_diagnostics_df(vs_fit))
```

## Fit an SOC-only projection

```{r}
soc_fit <- project_soc_only(
  data = analysis,
  arm = "arm",
  soc_level = "SOC",
  time = "time",
  event = "event",
  subgroup = "subgroup",
  tau = 365,
  hr_scenarios = c(0.65, 0.80, 1.00),
  target_delta_rmst = 30,
  prior_mean_log_hr = log(0.8),
  prior_sd_log_hr = 0.25,
  bootstrap = 10,
  seed = 200
)

summary(soc_fit)
```

```{r}
head(as_effects_df(soc_fit))
```

SOC-only results are always labeled as `Projection (assumption-based)`.

## Export machine-readable outputs

```{r}
out_dir <- tempfile(pattern = "cce-start-")
write_cce_results(vs_fit, out_dir)
list.files(out_dir)
```

The standard export set is:

- `results.json`
- `curves.csv`
- `effects.csv`
- `diagnostics.csv`

## Next steps

For a full synthetic walkthrough, see the bundled demo-data case study. For a
real public patient-level example, see the `survival::veteran` case study.
