---
title: "Public oncology data workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Public oncology data workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This article uses the public `survival::veteran` dataset as a compact
real-data example. It is not a production oncology registry, but it provides a
real patient-level time-to-event dataset with treatment assignment and baseline
covariates.

## Prepare the public dataset

```{r}
library(cce)
library(survival)

data(veteran, package = "survival")

veteran2 <- veteran
veteran2$arm <- ifelse(veteran2$trt == 1, "SOC", "A")
veteran2$event <- veteran2$status
veteran2$subgroup <- as.character(veteran2$celltype)
veteran2$prior <- factor(veteran2$prior)

head(veteran2)
```

## Fit a VS comparison

```{r}
vs_fit <- fit_cce_vs(
  data = veteran2,
  arm = "arm",
  time = "time",
  event = "event",
  covariates = c("karno", "diagtime", "age", "prior", "subgroup"),
  subgroup = "subgroup",
  tau = 180,
  landmark_times = c(90, 180),
  bootstrap = 10,
  seed = 300
)

summary(vs_fit)
```

```{r, fig.width = 7, fig.height = 4}
plot(vs_fit, method = "iptw", subgroup = "All")
```

```{r}
head(as_effects_df(vs_fit))
```

## Create an SOC-only projection

For scenario planning, we can keep only the SOC rows and overlay
assumption-based proportional-hazards projections.

```{r}
soc_fit <- project_soc_only(
  data = veteran2,
  arm = "arm",
  soc_level = "SOC",
  time = "time",
  event = "event",
  subgroup = "subgroup",
  tau = 180,
  hr_scenarios = c(0.75, 0.90, 1.00),
  target_delta_rmst = 15,
  prior_mean_log_hr = log(0.85),
  prior_sd_log_hr = 0.20,
  bootstrap = 10,
  seed = 400
)

summary(soc_fit)
```

```{r, fig.width = 7, fig.height = 4}
plot(soc_fit, subgroup = "All")
```

## Interpretation notes

- VS-mode results are model-based causal estimates under standard identifying
  assumptions.
- SOC-only outputs are projections, not causal estimates.
- In real programs, diagnostics should be interpreted together with data
  provenance, treatment policy definitions, and endpoint adjudication rules.
