---
title: "Theory and design"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Theory and design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
if (requireNamespace("pkgload", quietly = TRUE)) {
  if (file.exists("DESCRIPTION")) {
    pkgload::load_all(".", export_all = FALSE, helpers = FALSE, attach_testthat = FALSE)
  } else if (file.exists("../DESCRIPTION")) {
    pkgload::load_all("..", export_all = FALSE, helpers = FALSE, attach_testthat = FALSE)
  } else {
    library(cce)
  }
} else {
  library(cce)
}
```

## Package scope

`cce` is designed for a narrow class of survival analyses where the practical
goal is to put VS-mode estimation and SOC-only scenario planning on one stable
output contract.

The package is built around three ideas:

- the source tables should be normalized and validated before modeling
- VS and SOC-only analyses should emit the same machine-readable outputs
- diagnostics and metadata should be first-class outputs, not afterthoughts

## Input contract

The input contract is explicit through `cce_spec()` and the four normalized
tables:

- `patient_baseline`
- `treatment_episodes`
- `outcomes`
- `biomarkers`

This is not just a convenience wrapper. The contract is what makes exclusion
rules, arm mapping, subgroup derivation, and output reproducibility stable
across repeated analyses.

```{r}
demo <- cce_demo_data(n = 80, seed = 7)
str(demo$spec, max.level = 1)
```

## VS workflow

The VS workflow is implemented in `fit_cce_vs()`. It returns standardized
survival outputs on a common schema for:

- `gformula`
- `iptw_km`
- `iptw_cox`

The practical target is not a single scalar estimate. The package keeps the
curve-level output, landmark contrasts, RMST summaries, and diagnostics aligned
on the same result object.

```{r}
vs_fit <- fit_cce_vs(
  data = demo$analysis_data,
  arm = "arm",
  time = "time",
  event = "event",
  covariates = c("age", "sex", "stage_or_risk", "ps"),
  subgroup = "subgroup",
  tau = 365,
  landmark_times = c(180, 365),
  bootstrap = 5,
  seed = 21
)

head(as_effects_df(vs_fit))
```

### Why two IPTW labels exist

`cce` keeps two IPTW-related labels on purpose:

- `iptw_km`: weighted Kaplan-Meier style marginal curves
- `iptw_cox`: weighted Cox-based curves

This avoids a common ambiguity where an output labeled only as `IPTW` can refer
either to weighted marginal survival or to a weighted model-based estimator.

## SOC-only workflow

The SOC-only workflow is implemented in `project_soc_only()`. It starts from
the observed SOC survival pattern and projects comparator curves under
proportional-hazards assumptions.

```{r}
soc_fit <- project_soc_only(
  data = demo$analysis_data,
  arm = "arm",
  soc_level = "SOC",
  time = "time",
  event = "event",
  subgroup = "subgroup",
  tau = 365,
  hr_scenarios = c(0.70, 0.85, 1.00),
  target_delta_rmst = 20,
  prior_mean_log_hr = log(0.85),
  prior_sd_log_hr = 0.20,
  bootstrap = 5,
  seed = 55
)

head(as_effects_df(soc_fit))
```

SOC-only results are projections. The package makes that explicit in the result
label and in the exported metadata.

## Diagnostics and fail rules

The package treats diagnostics as part of the primary product. `fit_cce_vs()`
returns overlap and weighting summaries together with fail flags and warning
flags.

```{r}
head(as_diagnostics_df(vs_fit))
```

The operational rule is simple:

- if diagnostics are acceptable, results are returned as standard outputs
- if diagnostics fail, the object is labeled for reference-only interpretation

This is intended to prevent silent over-interpretation of unstable weighted
analyses.

## Output contract

Both workflows are designed to feed the same export layer:

- `curves.csv`
- `effects.csv`
- `diagnostics.csv`
- `results.json`

```{r}
temp <- tempfile(pattern = "cce-design-")
write_cce_results(vs_fit, temp)
list.files(temp)
```

`results.json` stores the method labels, covariates, thresholds, subgroup
settings, spec payload, exclusion summary, validation report, and dataset
profile. This is the package's core reproducibility contract.

## Limits

`cce` does not currently try to solve the full survival-causal toolbox. In
particular, it does not yet implement:

- dynamic treatment regimes
- time-varying treatment assignment
- multi-arm comparator analysis on one output contract
- full production missing-data workflows

Those limits are deliberate. The package is trying to keep the contract for
counterfactual comparator work clear and stable before expanding scope.
